CES analysis for Paul Brockway rebound paper

### 2016-02-16 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now fitting with iXp for energy.

<<Models>>=
modelsFileName <- file.path("models", "Brockway2015Models.rds")
if (!rerunModels){
  # load from the file on disk
  models <- readRDS(modelsFileName)
} else {
  # re-run the models and save to disk.
  # In RStudio, be sure to set the working directory to the source file directory.
  models <- lapply(countries, function(coun){
    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
  })
  names(models) <- countries
  # Save the models.
  saveRDS(models, file = modelsFileName)
}
@

@@

>>>>

<<Models>>=
modelsFileName <- file.path("models", "Brockway2015Models.rds")
modelsiXpFileName <- file.path("models", "Brockway2015ModelsiXp.rds")
if (!rerunModels){
  # load from the file on disk
  models <- readRDS(modelsFileName)
  modelsiXp <- readRDS(modelsiXpFileName)
} else {
  # re-run the models and save to disk.
  # In RStudio, be sure to set the working directory to the source file directory.
  models <- lapply(countries, function(coun){
    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
  })
  names(models) <- countries
  # Save the models.
  saveRDS(models, file = modelsFileName)

  # Now models using iXp instead of iU
  modelsiXp <- lapply(countries, function(coun){
    return(cesModel(iY ~ iK + iL + iXp + iYear, filter(historicalData, Country == coun, nest = 1:3)))
  })
  names(modelsiXp) <- countries
  # Save the models.
  saveRDS(modelsiXp, file = modelsiXpFileName)
}
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Primary Exergy} 
\label{sec:primary_exergy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We can also fit to historical data using quality-adjusted $kl$ and unadjusted $e$
in the form of primary exergy ($iXp$). 
Here are the results.

<<iXp, echo=TRUE>>=
# UK
modelsiXp$UK
# US
modelsiXp$US
# CN
modelsiXp$CN

# sse for each model

# UK
sum(resid(modelsiXp$UK)^2)
# US
sum(resid(modelsiXp$US)^2)
# CN
sum(resid(modelsiXp$CN)^2)

# Compare to sse for models that use iU
# UK
sum(resid(models$UK)^2)
# US
sum(resid(models$US)^2)
# CN
sum(resid(models$CN)^2)

@
